Hydras \& Co.

### 2021-12-28 doc/hydras.tex
comment out the watermark text
remove the book's subtitle
new title page

\documentclass[twoside,a4paper]{book}
\usepackage{alltt}
\usepackage{multind}
\usepackage{hyperref}
\usepackage{url}
\usepackage{xcolor, fancyvrb, mdframed}
\usepackage{amsmath}
%\usepackage{fancyhdr}
\usepackage{varioref}
\usepackage{synttree, proof, centernot}
\usepackage[firstpage]{draftwatermark}
\usepackage{verbatim}
\usepackage[note]{marginote}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{float}
\usepackage{threeparttable}
\usepackage{fontspec}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{placeins}
\usepackage{tikz}
\usepackage{tikzsymbols}
\usetikzlibrary{arrows}
\usepackage{graphicx}
\usepackage{amsmath,mathdots,dsfont}
\usepackage{amssymb}
\usepackage{newunicodechar}
\usepackage{theorem}
\usepackage{xspace}
\usepackage{texments}
%%% for movies by alectryon
\usepackage{movies/snippets/assets/alectryon}
\usepackage{movies/snippets/assets/pygments}

@@

\SetWatermarkLightness{0.8}
\definecolor{lightorange}{rgb}{1,0.9,0.9}
\SetWatermarkScale{0.35}
\SetWatermarkText{Work Continuously in Progress}
\SetWatermarkColor{lightorange}

@@

\title{Hydras \& Co.\\ Formalized mathematics in \coq for inspiration and entertainment}
%\pagestyle{fancy}
%\fancyhead{Hydras, Ordinals, \& Co.}
\makeindex{coq}
\makeindex{maths}
\makeindex{hydras}
\makeindex{additions}
\makeindex{primrec}
\begin{document}
\maketitle

% \cleardoublepage

% \mbox{~}
\clearpage
% \newpage
% \mbox{~}
\begin{quote}
 \emph{(Aprieta el bast\'on con las dos manos, se yergue un tanto,
casi con entusiasmo)} ¡Caramba! Claro \dots{} los n\'umeros
transfinitos, Kantor \dots{}

>>>>

\documentclass[twoside,a4paper]{book}
\usepackage{alltt}
\usepackage{multind}
\usepackage{hyperref}
\usepackage{url}
\usepackage{xcolor, fancyvrb, mdframed}
\usepackage{amsmath}
%\usepackage{fancyhdr}
\usepackage{varioref}
\usepackage{synttree, proof, centernot}
%\usepackage[firstpage]{draftwatermark}
\usepackage{verbatim}
\usepackage[note]{marginote}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{float}
\usepackage{threeparttable}
\usepackage{fontspec}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{placeins}
\usepackage{tikz}
\usepackage{tikzsymbols}
\usetikzlibrary{arrows}
\usepackage{graphicx}
\usepackage{amsmath,mathdots,dsfont}
\usepackage{amssymb}
\usepackage{newunicodechar}
\usepackage{theorem}
\usepackage{xspace}
\usepackage{texments}
%%% for movies by alectryon
\usepackage{movies/snippets/assets/alectryon}
\usepackage{movies/snippets/assets/pygments}

@@

% \SetWatermarkLightness{0.8}
\definecolor{darkblue}{rgb}{0,0.1,0.7}
% \SetWatermarkScale{0.35}
% \SetWatermarkText{Work Continuously in Progress}
% \SetWatermarkColor{lightorange}

@@

\title{Hydras \& Co.}
%\pagestyle{fancy}
%\fancyhead{Hydras, Ordinals, \& Co.}
\makeindex{coq}
\makeindex{maths}
\makeindex{hydras}
\makeindex{additions}
\makeindex{primrec}
\begin{document}
\begin{titlepage}
   \begin{center}
       \vspace*{1cm}

       \textbf{\LARGE Hydras \& Co.}

       \vspace{0.5cm}
        Formalized mathematics in \coq for inspiration and entertainement

       \vspace{1.5cm}

       \emph{Pierre Castéran, LaBRI, Univ. Bordeaux, CNRS UMR 5800, \\ With contributions by Yves Bertot, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Karl Palmskog, Clément Pit-Claudel, and Théo Zimmermann. \\ The formalization of primitive recursive functions was originally authored by Russel O'Connor\cite{OConnor05}.}

 \vfill
        \today

      \end{center}
\vfill
      \centering
      \includegraphics[width=13cm]{epsilon0.jpg}
      \centerline{\emph{\small {\color{darkblue}Ordinal numbers (less than $\Gamma_0$)}}}
\end{titlepage}

\clearpage
\newpage
% \mbox{~}
\begin{quote}
 \emph{(Aprieta el bast\'on con las dos manos, se yergue un tanto,
casi con entusiasmo)} ¡Caramba! Claro \dots{} los n\'umeros
transfinitos, Kantor \dots{}
